---
title: "Alcohol vs Seat choice"
author: "Jonathan Urbano"
date: "June 7, 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data
```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))
```  
  

```{r}
library(ggplot2)

ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot() +
  labs(title = "Boxplot of Alcohol by Seat")

```

The graphs show that the students in the back of the class have much greater results than the ones that sit in the front or middle, meaning that the ones that sit in the back have higher liklihood of picking up alcohol.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

In the data it shows that the people that in the middle are drinking a lot more then the people im the back and the front. Also in the data you can see that min all equals 0 but in the median it shows that the back have 4 and the front has 0 and the middle has 1. Thats a hugh difference. most of the people are sitting in the middle which is 83 and the rest and evened out in the back and the front and you can find that in the letter "n".


## Inferential Tests
```{r}

model1 <- aov(alcohol~Seat,data=davisdata)

summary.aov(model1)

```

This graph shows a significant result since the numbers are smaller than 0.05

```{r}

plot(TukeyHSD(model1))

```

This graph shows the difference between how much each seat drinks. We learned that the student in the front and the middle of the class drink about the same amountbut the kids in the back take over the amount drank by the front and middle seats so they drank the most

## Conclusions
Because the students in the back of the class are shown to drink much more than the kids in the front and middle parts. The graphs have shown that there is a night and day difference from the kids who sit in the back, making them more suceptible to alcoholism. 

